Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-30 ms.tex
show that the read noise goes like 1/sqrt(n) for integration to integration.

The timescale of most interest to studying atmospheres is the transit duration when trying to assess the stability.
The transit durations for most exoplanets considered is several hours long.
We therefore quantify error source over 1 hour duration.
If the smallest stripe subarray is used, frame time is 0.34 seconds.
For simplicity, assuming a duty cycle of 80\% due to detector resets, there are 8460 frames over which to average read noise.
Therefore, the final read noise is only expected to be 1.4 ppm over a 1 hour timescale if each frame is statistically independent.

@@

>>>>

The timescale of most interest to studying atmospheres is the transit duration when trying to assess the stability.
The transit durations for most exoplanets considered is several hours long.
We therefore quantify error source over 1 hour duration.
If the smallest stripe subarray is used, frame time is 0.34 seconds.
For simplicity, assuming a duty cycle of 80\% due to detector resets, there are 8460 frames over which to average read noise.
Therefore, the final read noise is only expected to be 1.4 ppm over a 1 hour timescale if each frame is statistically independent.
In section \ref{sec:darkBaseline}, we show from dark frames, that the read noise is statistically independent from integration to integration.

@@

\clearpage
\subsubsection{Dark Baseline Test}\label{sec:darkBaseline}
In Figure \ref{fig:darkBaselineAllan}, we show that the noise in a series of dark integrations averages with the square root of the number of integrations.
While 1/f is highly correlated within an aperture and results in a large value.

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{allan_var_removelinear_False_darkBaseline.pdf}
\caption{The noise in a dark exposure scales with 1/$\sqrt{N}$ for $N$ exposures, as would be expected for white noise.
Here, we have assumed an illumination of 3.7$\times10^8$ DN to convert the noise in DN to a relevant ppm for illuminated data.
While 1/f noise substantially increases the noise over the assumption that each pixel's read noise is statistically independent, each integration is statistically independent.
}\label{fig:darkBaselineAllan}
\end{figure*}
